
\input ./moderncv
% ==================== Main text ====================>
\starttext
\placehead

% self profile
\subject{Self Assessment}
More than 12 years experience worked in product R&D department of Ether / SDH transmission equipment.
Very adaptable and Good at leaning.
Diligent; with sureness; responsible; everytime fulfil my duties to my own work.
Patient; have holding capacity to pressure and setback.

Experienced on GNU/Linux, from bootloader, kernel/driver, to application, all are covered.
Experienced on FPGA development, focused on Image processing and Motor control.

% work experience
\subject{Work Experience}

\cvworkexp{2012 ~ today}{Nanjing Jilong Optical Communication Co., Ltd}{R&D}{Nanjing}{Manager}{
Build up Tech Platform based on GNU/Linux;

Responsible for new staff technical training;

Presided over the design and development of the next generation splicing control system.
Through motor controlling, image processing, arc controlling,
implement fusion splicing, heating, arc adjustment, system testing, dust checking, auto focusing, etc.

tech involved: state machine, socket communication, json message, xml configuration, image processing, video recording, etc.
FPGA is responsible for image sampling, format converting, image scaling, image overlaying, motor controlling, etc.

Dev Env：Xilinx Vivado, Archlinux, gitlab, poky(yocto), opencv, boost, {\TeX}live, Qt, maxima, android studio.

Programming Language: verilog, python, Makefile, Con\TeX t, C++11, C, bash, lua

Hardware Platform: arm, s3c6410, zynq7020
}

\cvworkexp{2010 ～ 2012}{Insigma}{Iot BU}{Hangzhou}{}{
\startigBase
\item Responsible for pre-research and construction of software department infrastructure;
\item Participate in the overall design of the software platform;
\item Responsible for the design and development of the low-level software platform;
\item Research and use of open source software / projects, design and development of related supporting tools;
\item Responsible for some recruitment and technical training;
\item As SA735 product development representative, responsible for its software development and release management;
\item Participate SN6500 product software design and development;
\item Responsible for the data center's preliminary research work, including hardware selection, distributed file system, distributed database.
\stopigBase

Development environment is mainly Linux and C/C++.
Development work including but not limited to:
\startigBase
\item Embedded OS build system optimus (based on yocto),
Mainly in order to solve the problem of product differentiation, one platform supporting multiple products.
\item GUI compiling tool：Tai Chi diagram (based on wxPython),
providing a GUI to display dependencies between packages,
and executing recursive compilation.
\item Dual redundancy backup system design and development (including supporting tool).
\item Process Execution Model,
Driver framework (mainly used for seamless switching between the user mode and kernel mode)
Process and equipment management module,
FPGAs/CPLDs Loading module.
\item mm/md used under GNU/Linux (same command used in uboot).
\item scripts used to generate UBIFS image.
\item p2020/mpc8315 (freescale/powerpc）related bsp dev.
\item \dots
\stopigBase
}

\cvworkexp{2009 ～ 2010}{NSN}{NGMGW}{Hangzhou}{team leader of TDM group}{
Responsible for TDM related service, including business needs analysis,
writing related documents and software design and development, e.g.
SDH/PDH configuration management, clock management, and the corresponding redundancy, etc.
}

\cvworkexp{2007 ～ 2009}{UT Starcom}{ONS}{Hangzhou}{SW engineer}{
mainly woring for product NR40K:
\startigBase
\item low-order XC chip research and development;
\item development of XC board, hybrid fiber board;
\item development of hot-backup, SSF, MAPS;
\item development and maintenance of: configuration management, algorithm module;
\item interrupt management, timer managment;
\stopigBase

Development environment: windows/vxworks, C/C++.
}

\cvworkexp{2005 ～ 2006}{HarbourNetworks}{R&D switch product line}{Beijing}{SW engineer}{
mainly working on product BH68 series switcher:

Responsible for development of QoS/ACL, including maintenance of application/driver,
new requirement of MassACL, IPv6, fucntion testing of new chip, firebolt/easyridar from broadcom.

Responsible for development and maintenance of DHCP module.

Development environment: windows/vxworks, C/C++.
}

% education
\subject{Education}

\cventry{2004 ～ 2007}{
{\bf Master} \hskip 1em {Xidian University} \hskip 1em {Xi'an} \hskip 1em {Computer science and technology}
}

\cventry{2000 ～ 2004}{
{\bf Bachelor} \hskip 1em {Xidian University} \hskip 1em {Xi'an} \hskip 1em {Computer science and technology}
}

% language
\subject{Language}

\cventry{English}{CET-6}

\stoptext
